An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-06-19 Article/EconGrowth2.Rnw
Added a section on LINEX trajectories. Also discussed alpha, beta, and gamma constraints.

>>>>

The LINEX model coefficients $a_0$ and $c_t$ imply time-dependent
values of $\alpha$, $\beta$, and $\gamma$ as given by the following equations~\citep{Warr:2012cg}:

\begin{equation} \label{eq:LINEX_alpha}
  \alpha = \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \;,
\end{equation}

\begin{equation} \label{eq:LINEX_beta}
  \beta = \frac{l}{y} \frac{\partial y}{\partial l} = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
\end{equation}

\noindent{}and

\begin{equation} \label{eq:LINEX_beta}
  \gamma = \frac{e}{y} \frac{\partial y}{\partial e} 
         = 1 - a_0 \left[ \frac{e}{k} + c_t \frac{l}{e} \right] 
         = 1 - \alpha - \beta \;.
\end{equation}

\noindent Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
If the trajectory stays within the triangle, 
the constraints of $\alpha > 0$, $\beta > 0$, and $\gamma > 0$ are respected.  
Conversely, if the trajectory goes outside the triangle, one of the constraints has been violated.

The following graphs shows trajectories for China and Iran.

<<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
dataCN <- fortify(OrigModels$CN$linex$`iK+iL+iQ`)
triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@

<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=2, fig.cap="LINEX trajectory for Iran.">>=
dataIR <- fortify(OrigModels$IR$linex$`iK+iL+iQ`)
triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@

Iran is the only country for which the trajecotry stays within the triangle for the 
entire time period.
Thus, in our fitted models, the LINEX model is, for the most part, 
violating constraints on $\alpha$, $\beta$, and $\gamma$.
If the LINEX model were made to respect the constraints on $\alpha$, $\beta$, and $\gamma$,
it would fit worse than it already does for those countries where
the constraints are violated (that is, for every country except Iran).
We did nothing to correct this situation, because it is not clear what could be done.
Constraining $\alpha = 0$ in the case of China would imply that either
$a_0$ or $c_t$ or both varied with time.
At that point, $a_0$ and $c_t$ are no longer fitted parameters of the model, 
and we have a different model: it is no longer LINEX.
